Comparative Evaluation of Spark and Flink Stream Processing

### 2017-02-19 paper/paper.tex
first version of introduction section

\end{abstract}
Recent years have witnessed a big development improvements of Big Data frameworks such as Apache Spark, Apache Flink. For example, both frameworks support real-time
streaming processing. While which platform is the best still an open question. 
In this paper, we provide a performance comparison of streaming data processing in Spark and Flink, by measuring different performance metrics, namely latency and throughput. The experiment is done using multiple streaming workloads over real-world datasets.
\section{Introduction}

\par Big Data is now one of the hot topic in Information Technology, it has gained increasing attention of professionals in industry and academics, since the amount of data we generate is increasing. Moreover, recent years showed a rapid development of Big Data frameworks such Hadoop, Spark, Flink.    
 \par The Big Data is a method to process not just only just large datasets (volume), but also that arrives in high rate (velocity), and it comes in all kind of formats (variety) \cite{svs}.

\par The purpose of this paper is to provide a comparative experimental evaluation of throughput, latency (i.e., performance) of stream processing in Spark and Flink. We use a dataset of airplanes trajectories provided in the context of Datacron project\footnote{\url{http://www.datacron\-project.eu/}}, in order to simulate real-world use cases. Using multiple streaming data workloads we try to cover the main programming API differences between the both frameworks. Informally,  this work aims to help developer to determine which platform to chose in production.

>>>>

\end{abstract}
Recent years have witnessed a big development improvements of Big Data frameworks such as Apache Spark and Apache Flink. For example, both frameworks support real-time
streaming processing. While which platform is the best still an open question. 
In this paper, we provide a performance comparison of streaming data processing in Spark and Flink, by measuring different performance metrics, namely latency and throughput. The experiment is done using multiple streaming workloads over real-world datasets.
\section{Introduction}

\par Big Data is now one of the hot topics in Information Technology, it has gained increasing attention of professionals in industry and academics, since the amount of data we generate is increasing exponentially. Moreover, recent years showed a rapid development of Big Data frameworks such as Spark and Flink that provide more and efficient data processing capabilities.
 \par The Big Data is a method to process not just only just large datasets (volume), but also that arrives in high rate (velocity), and it comes in all kinds of data format (variety) (i.e., 3Vs of Big Data (Volume, Velocity, Variety))\cite{svs}.

\par The processing models of Big Data are Batch and Stream processing, Batch processing is a way to handle large volumes of data (e.g., processing of historical transactions), is more concerned with throughput. While the Stream processing  is to manages fast and continues data (real-time) and processes it as it arrives (e.g., fraud detection and network monitoring applications), where the low latency is required.

\par The purpose of this paper is to provide a comparative experimental evaluation of throughput, latency (i.e., performance) of stream processing in Apache Spark and Apache Flink. We use a dataset of airplanes trajectories provided in the context of Datacron project\footnote{\url{http://www.datacron-project.eu/}}, in order to simulate real-world use cases. Using multiple streaming data workloads we try to cover the main programming API differences between the both frameworks. Informally,  this work aims to help developer to determine which platform to choose in production.
